A Review of Crime Data and how GDP and Population Affects Crime Rates

### 2017-03-08 paper/paper.Rmd
finished

---
output: pdf_document
  #pdf_document:
    #citation_package: natbib
    #keep_tex: true
    #fig_caption: true
    #latex_engine: pdflatex
    #template: ~\INFO370\svm-r-markdown-templates\svm-latex-anon-ms
title: "A review of Crime data and how GDP affects Crime Rates"
author:
- Kai Yoshino, University of Washington
- Isabella Spaletta, University of Washington 
- Chrisopther Ross, University of Washington
- Marisa Nanaku, University of Washington

>>>>

---
output: pdf_document
  #pdf_document:
    #citation_package: natbib
    #keep_tex: true
    #fig_caption: true
    #latex_engine: pdflatex
    #template: ~\INFO370\svm-r-markdown-templates\svm-latex-anon-ms
title: "A Review of Crime Data and how GDP and Population Affects Crime Rates"
author:
- Kai Yoshino, University of Washington
- Isabella Spaletta, University of Washington 
- Chrisopther Ross, University of Washington
- Marisa Nanaku, University of Washington
